% ************************** Thesis Acknowledgements *****************************

\begin{acknowledgements}      

First and foremost I would like to thank my supervisor, Professor Zoubin Ghahramani.
He has been very supportive whilst allowing my mind to wander as much as I desired.
Working with Zoubin has made PhD life quite the antithesis of the vision presented in PhD comics and other derogatory depictions.

Secondly I would like to thank all of my collaborators.
Special thanks go to Peter Orbanz and Daniel Roy for helping me find and co-supervising my first project and subsequent investigation.
I am also very glad to have worked with David Duvenaud on my later projects; our contrasting styles of working and writing were a great source of synergy.
I would also like to thank Roger Grosse for showing me a higher standard of research programming, Joshua Tenenbaum for his infectious enthusiasm and Jos\'{e} Miguel Hern\'{a}ndez-Lobato for his unequaled diligence.

I would also like to thank everyone at the computational and biological learning group for creating such an enjoyable working environment.
Special mentions go to Carl Rasmussen for sharing his knowledge of Gaussian processes, Alex Matthews for joining me in discussions on the philosophy of statistics, Yarin Gal for an endless source of (productive) contrarianism and Alex Davies for teaching me the ways of data mining (AHRF) and for being a most excellent friend.

Finally, I would like to thank all of the other friends I made during my studies.
In particular I would like to thank Alexa Pohl and Matthew Griffiths for keeping conversation scholarly longer than most, Will Sonnex for valiant efforts to explain the elegance of type theory, and Rosie Lintott for reminding many of us that there is more to life than mathematics.

\end{acknowledgements}
